### 2017-04-04 paper/oopsla17-submission/learning.tex
references

\subsubsection{Contextual syntactic features}
These are similar to local syntactic features, but lifted to describe the
parent and children of the current expression.
%
For example, the \IsCaseListP feature in \autoref{tab:sumList} describes
whether current expression's \emph{parent} matches on a list.
%
If a particular $e$ does not have children (\eg a variable $x$) or a
parent (\ie the root expression), we leave the corresponding features
disabled.
%
This gives us a notion of the \emph{context} in which an expression
occurs, similar to the \emph{n-grams} commonly used in linguistic
models \citep{Hindle2012-hf,Gotterbarn1998-gc}.

>>>>

\subsubsection{Contextual syntactic features}
These are similar to local syntactic features, but lifted to describe the
parent and children of the current expression.
%
For example, the \IsCaseListP feature in \autoref{tab:sumList} describes
whether current expression's \emph{parent} matches on a list.
%
If a particular $e$ does not have children (\eg a variable $x$) or a
parent (\ie the root expression), we leave the corresponding features
disabled.
%
This gives us a notion of the \emph{context} in which an expression
occurs, similar to the \emph{n-grams} commonly used in linguistic
models \citep{Hindle2012-hf,Gabel2010-el}.
